---
title: "Churn prediction"
author: "Arm"
date: "2024-01-16"
output: html_document
---

<br>

### Load library

```{r, message=FALSE}
library(caret)
library(tidyverse)
```

<br>

### Load data

```{r, message=FALSE}
read_csv("churn.csv")
churn <- read_csv("churn.csv")
```

<br>

### Review data

```{r}
glimpse(churn)
```

<br>

### Prepare data

**Change column `churn`, `internationalplan`, `voicemailplan` to factor**


```{r}
df <- churn %>%
    select(churn, internationalplan, voicemailplan, numbervmailmessages, totaldaycalls, totaldaycharge) %>%
    mutate(churn = factor(churn),
           internationalplan  = factor(internationalplan),
           voicemailplan = factor(voicemailplan))

glimpse(df)

```

<br>

### Create function split_data(data, size)

**split_data()** รับ input 2 ตัว

**data** = data set

**size** = percent of train data


```{r}
split_data <- function(data, size) {
  set.seed(42)
  n <- nrow(data)
  numrow <- sample(n, size = size*n)
  train_data <- data[numrow, ]
  test_data <- data[-numrow, ]
  return(list(train_data, test_data))
}
```

<br>

### Split data

```{r}
split <- split_data(df, 0.8)

train_data <- split[[1]] # train data 
test_data <- split[[2]] # test data 
```

<br>

**Train data**
```{r}
glimpse(train_data)
```

<br>

**Test data**
```{r}
glimpse(test_data)
```

<br>

### Train model

**y = f(x1, x2, x3, x4, x5)**

**y** = churn

**x1** = internationalplan

**x2** = voicemailplan 

**x3** = numbervmailmessages

**x4** = totaldaycalls 

**x5** = totaldaycharge 

<br>

```{r}
glm_model <- train(churn ~ internationalplan + voicemailplan + numbervmailmessages + totaldaycalls + totaldaycharge, 
                   data = train_data, 
                   method = "glm" )

glm_model
```

<br>

### Score and evaluate

```{r}
p <- predict(glm_model, newdata = test_data)
```

<br>

### Accuracy Test data

```{r}
accuracy <- mean(p == test_data$churn)
accuracy
```

<br>

### Print result

```{r}
library(glue)
```

<br>

```{r}
glue("Train Accuracy: {round(glm_model$results[[2]], 4)} \n Test Accuracy : {accuracy}")

```







